### 2021-11-02 tikz/priors-tradeoffs.tex
draft figures to meet with Klaus

\begin{document}
\begin{tikzpicture}[auto, family=\sffamily]
  \node[model] (a) at (0,0) {
    (a)\\
    \includegraphics[height=2.5in]{../plots/historic_surge.pdf}
  };
  \node[model] (b) at (8.5,0) {
    (b)\\
    \includegraphics[height=2.5in]{../plots/surge_cdf.pdf}
  };
\end{tikzpicture}
\end{document}

>>>>

\begin{document}
\begin{tikzpicture}[auto, family=\sffamily]
  \node[model] (a) at (0,0) {
    (a)\\
    \includegraphics[height=2.5in]{../plots/lsl_priors.pdf}
  };
  \node[model] (b) [right=0.1in of a] {
    (b)\\
    \includegraphics[height=2.5in]{../plots/tradeoffs_height_damages_byprior.pdf}
  };
  \node[model] (c) [right=0.1in of b]{
    (c)\\
    \includegraphics[height=2.5in]{../plots/tradeoffs_height_totalcost_byprior.pdf}
  };
  \node[model] (d) [right=0.1in of c]{
    (d)\\
    \includegraphics[height=2.5in]{../plots/tradeoffs_height_iqr_byprior.pdf}
  };
\end{tikzpicture}
\end{document}
